Towards Patient-Specific Neural Field Modeling using Micro-Electrode Data

### 2011-02-07 ltx/data_paper/DataPaper.tex
edits to M step

@@

where $ \mathbf E_{\boldsymbol \Theta'}$ denotes expectation with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \Theta') $ where $\boldsymbol \Theta'$ is the current parameter estimate. Re-writing $\mathcal Q$-function in terms of joint distribution components gives

@@

 \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\boldsymbol \Sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \xi)+\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right],

@@

 $p(\mathbf x_0)$ is not function of parameter set and therefore $\mathcal Q$-function can be rewritten as

@@

\mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\boldsymbol \Sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\xi)\right]+\mathrm{const}

>>>>

\begin{align}\label{eq:QFunction}

@@

where $ \mathbf E_{\boldsymbol \Theta'}$ denotes expectation with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \Theta')$, and $\boldsymbol \Theta'$ is the current parameter estimates. Substituting  \ref{eq:jointdistribution} in \ref{eq:QFunction} gives

@@

 \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta, \sigma_d)+\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right],

@@

 $p(\mathbf x_0)$ is not a function of parameter set and therefore $\mathcal Q$-function can be rewritten as

@@

\mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1};\boldsymbol \sigma_{\epsilon})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta ,\sigma_d)\right]+\mathrm{const}
